---
title: "Shiny Meta Weather"
output: 
  flexdashboard::flex_dashboard:
    theme: simple
    orientation: columns
    vertical_layout: fill
    source_code: "https://github.com/stenzei/ShinyWeather"
runtime: shiny    
---
  
```{r global, include=FALSE}
library(flexdashboard)
library(highcharter)
library(leaflet)
library(shiny)
library(tidyverse)

source("src/model/R6-forecast-dta.R")
forecast_dta <- forecast_dta_R6$new("dta")
```

Forecast 
=========================================

Column {data-width=200}
-----------------------------------------

### Controls

```{r} 
selectizeInput("city", "Choose city:", 
               choices = forecast_dta$get_all_cities(),
               selected = c("Göttingen"),
               multiple = TRUE,
               options = list(hideSelected = TRUE,
                              maxItems = 1))
checkboxInput("all_cities", "Show all available cities")
radioButtons("dta_source", "Choose data source:", 
             choices = list("mean of all" = "mean of all",
                            "Provider A" = "www.weather.com",
                            "Provider B" = "www.wetter.com",
                            "Provider C" = "www.wetter.de",
                            "Provider D" = "www.wetterkontor.de"), 
             selected = "mean of all")
sliderInput("number_of_days", "Forecast horizon in days:", 
              min = 1, max = 7, value = 5,step = 1, ticks = FALSE)
```

Click the blue marker(s) and see weather data for that city on the selected day.
As data may differ between forecast providers you can choose a particular source 
or just view the mean value of the four sources. See the [About](#about) tab
for further information.


Column {data-width=350}
-----------------------------------------

### Map {data-height=500}

```{r}
source("src/modules/map-tile.R")
mapTileUI("forecast_map")
callModule(mapTile, "forecast_map", 
           reactive(input$city), 
           reactive(input$dta_source),
           reactive(input$all_cities),
           forecast_dta)
```

### Forcast {data-heigth=500}

```{r} 
source("src/modules/table-tile.R")
tableTileUI("forecast_table")
callModule(tableTile, "forecast_table", 
           reactive(input$city), 
           reactive(input$dta_source),
           reactive(input$number_of_days),
           forecast_dta)
```

Column {data-width=550}
-----------------------------------------

### Chart

```{r} 
source("src/modules/chart-tile.R")
chartTileUI("forecast_chart")
callModule(chartTile, "forecast_chart", 
           reactive(input$city), 
           reactive(input$dta_source),
           reactive(input$number_of_days),
           forecast_dta)
```


Forecast quality
=========================================

Row
-------------------------

### Mean Difference of Temperature (K)

```{r}
source("src/modules/quality-tile.R")
qualityTileUI("md_temperature_chart")
callModule(qualityTile, "md_temperature_chart", 
           forecast_dta, "MEAN_DIFF_TEMPERATURE")
```

### Mean Difference of Rain Probability (%)

```{r}
qualityTileUI("md_rain_prob_chart")
callModule(qualityTile, "md_rain_prob_chart", 
           forecast_dta, "MEAN_DIFF_RAIN_PROB")
```

Row
-------------------------

### Mean Difference of Wind Speed (km/h)

```{r}
qualityTileUI("md_wind_speed_chart")
callModule(qualityTile, "md_wind_speed_chart", 
           forecast_dta, "MEAN_DIFF_WIND_SPEED")
```

### Mean Difference of Rain Ammount (l/m^2^)

```{r}
qualityTileUI("md_rain_ammount_chart")
callModule(qualityTile, "md_rain_ammount_chart", 
           forecast_dta, "MEAN_DIFF_RAIN_AMMOUNT")
```


Data
=========================================

### Data

```{r}
source("src/modules/data-tile.R")
dataTileUI("all_data")
callModule(dataTile, "all_data", forecast_dta)
```



About{#about}
=========================================

### A Shiny Weather dashboard 
The app allows to compare the forcast data from different providers and to assess 
__roughly__ its reliability. The data taken, is forcast data for around noon.
What "around noon" means differs among the providers. Further more, the data is
only scraped on the level of cities, therefore weather data for e.g. Berlin
can very. Thus, the data is __not really comparable__!

Nevertheless scraping could be improoved in a way that allows a reliable 
comparrison of forecast quality.

#### Data
The weather forecast data originates from four web sites for further analyses:

- [wetter.com](http://www.wetter.com), which provides weather data e.g. for 
[Spiegel Online](http://www.spiegel.de); 
- [wetter.de](http://www.wetter.de); 
- [weather.com](https://weather.com), which provides (among others) data for the 
Apple weather app;
- [wetterkontor.de](http://www.wetterkontor.de), which provides weather data e.g. 
for Bild.de.

The data is scraped from these web sites using 
[rvest](https://github.com/hadley/rvest) and 
[RSelenium](https://cran.r-project.org/web/packages/RSelenium/). Scraping 
happens on a daily basis and is not part of the dashboard.

