---
title: "Shiny Weather"
resource_files:
- dta/city-data_200.csv
- dta/city-geo-coordinates.csv
- dta/forecast-data-weather_com.csv
- dta/forecast-data-wetter_com.csv
- dta/forecast-data-wetter_de.csv
- dta/forecast-data-wetterkontor_de.csv
- dta/mapping-zip-city.csv
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    source: embed
    theme: simple
    vertical_layout: fill
---
  
```{r global, include=FALSE}
library(flexdashboard)
library(highcharter)
library(leaflet)
library(shiny)
library(tidyverse)

source("src/model/R6-forecast-dta.R")
forecast_dta <- forecast_dta_R6$new("dta")
```

Forecast 
=========================================

Column {data-width=350}
-----------------------------------------

### Forcast {data-heigth=500}

```{r} 
source("src/modules/table-tile.R")
tableTileUI("forecast_table")
callModule(tableTile, "forecast_table", 
           reactive(input$city), 
           reactive(input$dta_source),
           reactive(input$number_of_days),
           forecast_dta)
```

### Map {data-height=500}

```{r}
source("src/modules/map-tile.R")
mapTileUI("forecast_map")
callModule(mapTile, "forecast_map", 
           reactive(input$city), 
           reactive(input$dta_source),
           reactive(input$all_cities),
           forecast_dta)
```

Column {data-width=550}
-----------------------------------------

### Chart

```{r} 
source("src/modules/chart-tile.R")
chartTileUI("forecast_chart")
callModule(chartTile, "forecast_chart", 
           reactive(input$city), 
           reactive(input$dta_source),
           reactive(input$number_of_days),
           forecast_dta)
```

Column {data-width=200}
-----------------------------------------

### Controls

```{r} 
selectizeInput("city", "Choose city:", 
               choices = forecast_dta$get_all_cities(),
               selected = c("Göttingen"),
               multiple = TRUE,
               options = list(hideSelected = TRUE,
                              maxItems = 1))
checkboxInput("all_cities", "Show all available cities")
radioButtons("dta_source", "Choose data source:", 
             choices = c("mean of all", forecast_dta$get_sources()), 
             selected = "mean of all")
sliderInput("number_of_days", "Forecast horizon in days:", 
              min = 1, max = 7, value = 5,step = 1, ticks = FALSE)
```

Click the blue circles and see weather data for that city on the selected day.
As data may differ between forecast providers you can choose a particular source 
or just view the mean value of the four sources.



Forecast quality
=========================================

Row
-------------------------

### Mean Difference of Temperature (K)

```{r}
source("src/modules/quality-tile.R")
qualityTileUI("md_temperature_chart")
callModule(qualityTile, "md_temperature_chart", 
           reactive(input$dta_source2),
           forecast_dta, "MEAN_DIFF_TEMPERATURE")
```

### Mean Difference of Rain Probability (%)

```{r}
qualityTileUI("md_rain_prob_chart")
callModule(qualityTile, "md_rain_prob_chart", 
           reactive(input$dta_source2),
           forecast_dta, "MEAN_DIFF_RAIN_PROB")
```

Row
-------------------------

### Mean Difference of Wind Speed (km/h)

```{r}
qualityTileUI("md_wind_speed_chart")
callModule(qualityTile, "md_wind_speed_chart", 
           reactive(input$dta_source2),
           forecast_dta, "MEAN_DIFF_WIND_SPEED")
```

### Mean Difference of Rain Ammount (l/m^2^)

```{r}
qualityTileUI("md_rain_ammount_chart")
callModule(qualityTile, "md_rain_ammount_chart", 
           reactive(input$dta_source2),
           forecast_dta, "MEAN_DIFF_RAIN_AMMOUNT")
```

Column {data-width=200}
-----------------------------------------

### Controls

```{r} 
checkboxGroupInput("dta_source2", "Choose data source(s):", 
                   choices = forecast_dta$get_sources(), 
                   selected = forecast_dta$get_sources())
```

What you see is the forcast data from the days before the day you have chosen
for that particular day.



Forecast history
=========================================

Row
-------------------------

### History of Temperature Prediction

```{r}
source("src/modules/history-tile.R")
historyTileUI("hist_temperature_chart")
callModule(historyTile, "hist_temperature_chart", 
           reactive(input$city3),
           reactive(input$date3),
           reactive(input$dta_source3),
           forecast_dta, "TEMPERATURE")
```

### History of Rain Probability Prediction

```{r}
historyTileUI("hist_rain_prob_chart")
callModule(historyTile, "hist_rain_prob_chart", 
           reactive(input$city3),
           reactive(input$date3),
           reactive(input$dta_source3),
           forecast_dta, "RAIN_PROB")
```

Row
-------------------------

### History of Wind Speed Prediction

```{r}
historyTileUI("hist_wind_speed_chart")
callModule(historyTile, "hist_wind_speed_chart", 
           reactive(input$city3),
           reactive(input$date3),
           reactive(input$dta_source3),
           forecast_dta, "WIND_SPEED")
```

### History of Rain Ammount Predicition

```{r}
historyTileUI("hist_rain_ammount_chart")
callModule(historyTile, "hist_rain_ammount_chart", 
           reactive(input$city3),
           reactive(input$date3),
           reactive(input$dta_source3),
           forecast_dta, "RAIN_AMMOUNT")
```

Column {data-width=200}
-----------------------------------------

### Controls

```{r} 
selectInput("city3", "Choose a city:", forecast_dta$get_all_cities())
dateInput("date3", "Select a Date:", 
          value = lubridate::today(), 
          format = "dd.mm.yyyy")
checkboxGroupInput("dta_source3", "Choose data source(s):", 
                      choices = forecast_dta$get_sources(), 
                      selected = forecast_dta$get_sources())
```

What you see is the forcast data from the days before the day you have chosen
for that particular day.



About
=========================================
